Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Remove affiliation
Add \doctest command
This ensures that we always typeset in in the same way.

\newcommand{\hspec}{Hspec}

@@

\authorinfo{Simon HENGEL}
           {Freelance Software Developer}
           {sol@typeful.net}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\keywords Haddock, QuickCheck, doctest, Hspec

@@

In this paper, we explore how to apply BDD to Haskell.
We brought a test method from other programming language community and
integrated it with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck} as a BDD tool.
We also make use of \hspec{} inspired by RSpec~\cite{rspec} for
BDD in Haskell.

@@

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:for-users} and Section \ref{sec:doctest})
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using {\tt doctest} and \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

\noindent Our {\tt doctest} implementation
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

A good candidate for this is {\tt doctest} in Python community.
It extends Python's documentation strings so that they
can contain examples.
Examples can be tested by the Python interpreter.

@@

To be able to specify examples and properties for users, we propose to add new
markup to Haddock and to use {\tt doctest} integrated with QuickCheck. To
describe examples/properties for developers, we propose to use \hspec{} also
integrated with QuickCheck.

@@

\begin{itemize}
\item Define a new Haddock markup for examples.
\item Define a new Haddock markup for properties.
\item Bring {\tt doctest} from the Python community to the Haskell
community and integrate it with QuickCheck.
\end{itemize}

@@

Examples and properties in comments are automatically
tested by the {\tt doctest} command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{doctest}
\label{sec:doctest}

@@

\noindent We should execute {\tt doctest} to ensure no syntax errors.
Also, we specifies examples/properties for developers with \hspec{}:

@@

\noindent Cabals test feature can be used to automatically run tests.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and \hspec{} in a single cabal file.

@@

\noindent A driver for Doctest looks like so:

>>>>

\newcommand{\hspec}{Hspec}
\newcommand{\doctest}{Doctest}

@@

\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\keywords \doctest{}, Haddock, \hspec{}, QuickCheck

@@

In this paper, we explore how to apply BDD to Haskell.
We brought a test method from other programming language community and
integrated it with a Haskell-original test method.
In particular, we introduced \doctest{}~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck} as a BDD tool.
We also make use of \hspec{} inspired by RSpec~\cite{rspec} for
BDD in Haskell.

@@

\begin{itemize}
\item Introduced \doctest{} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:for-users} and Section \ref{sec:doctest})
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

\noindent Our \doctest{} implementation
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect
motivates Haskellers to write test code.

@@

A good candidate for this is \doctest{} in Python community.
It extends Python's documentation strings so that they
can contain examples.
Examples can be tested by the Python interpreter.

@@

To be able to specify examples and properties for users, we propose to add new
markup to Haddock and to use \doctest{} integrated with QuickCheck. To
describe examples/properties for developers, we propose to use \hspec{} also
integrated with QuickCheck.

@@

\begin{itemize}
\item Define a new Haddock markup for examples.
\item Define a new Haddock markup for properties.
\item Bring \doctest{} from the Python community to the Haskell
community and integrate it with QuickCheck.
\end{itemize}

@@

Examples and properties in comments are automatically
tested by the \doctest{} command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\doctest}
\label{sec:doctest}

@@

\noindent We should execute \doctest{} to ensure no syntax errors.
Also, we specifies examples/properties for developers with \hspec{}:

@@

\noindent Cabals test feature can be used to automatically run tests.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for \doctest{} and \hspec{} in a single cabal file.

@@

\noindent A driver for \doctest{} looks like so:
